Inference of seasonal forcings on reproduction numbers during epidemics

### 2020-04-18 PaperDraft.Rmd
figures

---
title: "Inference of seasonal forcings on reproduction numbers during epidemics"
author: "Fengyang Wang, Lu Lu, Ziyao Tian, Yi Xiao Zhang"
header-includes:
    - \usepackage{setspace}\onehalfspacing
output:
  pdf_document: default
  html_notebook: default
  rmarkdown::pdf_document:
    fig_caption: yes        
    includes:  
      in_header: preamble.tex
---

## Abstract

@@

## Introduction

@@

## Methodology

@@

### Incidence likelihood of the Thompson et al. model

@@

### Extension of Thompson et al. for $R$ subject to forcings

@@

### Using OLS and EpiEstim to check results

@@

### Data

@@

## Results

### Posterior Estimates

@@

\begin{center}
\includegraphics[width=0.5\textwidth]{plots/plot1.png}
\end{center}

```{r include=FALSE}
```

@@

### Estimates of $\theta$, transformed to climate-independent $R$ by date

\begin{center}
\includegraphics[width=.49\textwidth]{plots/plot5.png}
\end{center}

@@

### Estimated R in Various Provinces

\begin{center}
\includegraphics[width=.49\textwidth]{plots/plot6.png}
\includegraphics[width=.49\textwidth]{plots/plot7.png}
\includegraphics[width=.49\textwidth]{plots/plot8.png}
\includegraphics[width=.49\textwidth]{plots/plot9.png}
\end{center}

@@

### Interpretation

@@

## Discussion

@@

We would also like to look into statistical simulation models which consider intercity travel and geographic proximity. As our estimated $R$ is dependent on the serial interval number, it would also be worthwhile to see the sensitivity of our model with different values of serial interval number as did Flaxman et al. (2020)[6].

## Appendix

### Posterior of $\lambda$, location-dependent adjustment to $log(R)$

\begin{center}
\includegraphics[width=.49\textwidth]{plots/plot2.png}
\includegraphics[width=.49\textwidth]{plots/plot3.png}
\includegraphics[width=.49\textwidth]{plots/plot4.png}
\end{center}

@@

### Epsilon, idiosyncratic adjustment to log(R)

@@

### References

>>>>

---
title: "Inference of seasonal forcings on reproduction numbers during epidemics"
author: "Fengyang Wang, Lu Lu, Ziyao Tian, Yi Xiao Zhang"
organization: "STAT 440 Final Project"
header-includes:
    - \usepackage{setspace}\onehalfspacing
output:
  pdf_document:
    number_sections: true
  html_notebook: default
---

\textbf{Abstract}

@@

# Introduction

@@

# Methodology

@@

## Incidence likelihood of the Thompson et al. model

@@

## Extension of Thompson et al. for $R$ subject to forcings

@@

## Using OLS and EpiEstim to check results

@@

## Data

@@

# Results

## Posterior Estimates

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{plots/plot1.png}
\caption{Posterier distributions of beta}
\end{figure}

@@

## Estimates of $\theta$, transformed to climate-independent $R$ by date

\begin{figure}
\centering
\includegraphics[width=.49\textwidth]{plots/plot5.png}
\caption{Time series estimate of R with 0.8 confidence bands}
\end{figure}

@@

## Estimated R in Various Provinces

\begin{figure}
\centering
\includegraphics[width=.49\textwidth]{plots/plot6.png}
\includegraphics[width=.49\textwidth]{plots/plot7.png}
\includegraphics[width=.49\textwidth]{plots/plot8.png}
\includegraphics[width=.49\textwidth]{plots/plot9.png}
\caption{Time series estimates of R for Bergano, Milan, Rome, Venice}
\end{figure}

@@

## Interpretation

@@

# Discussion

@@

We would also like to look into statistical simulation models which consider intercity travel and geographic proximity. As our estimated $R$ is dependent on the serial interval number, it would also be worthwhile to see the sensitivity of our model with different values of serial interval number as did Flaxman et al. (2020)[6]. 
\newpage
# Appendix

## Posterior of $\lambda$, location-dependent adjustment to $log(R)$

\begin{figure}
\includegraphics[width=.49\textwidth]{plots/plot2.png}
\includegraphics[width=.49\textwidth]{plots/plot3.png}
\includegraphics[width=.49\textwidth]{plots/plot4.png}
\end{figure}

@@

## Epsilon, idiosyncratic adjustment to log(R)

@@

## References
